TODO:
\begin{itemize}
    \item Finalise introduction. It needs shortening.
    \item Add the simple "PRL" agent to background research;.
    \item finish Exploration survey
    \item Benchmarking!!!
    \item Sample efficiency analysis, complexity analysis
    \item ENSURE BACKGROUND EQUATIONS ARE CORRECT!!!!! Add general Bellman equation
    \item
Background research: Have I ...

    Explained the problem clearly?
    Identified relevant areas for investigation and discussed them in report under appropriate headings and critically?
    Reviewed previous attempts to solve this and similar problems?
    Justified any claims made using credible primary or secondary sources?


Methods: Is it clear that ...

    The solution exists?
    I have produced the deliverables specified?
    Appropriate steps or standards were taken to ensure a quality output (e.g. design documentation, comments in code)?
    The challenges were clearly articulated?


Results and Discussion: Is it clear that ...

    Appropriate tests and evaluation were conducted and analysed to validate the quality of deliverables within the remit of the project?
    There are objective criteria for evaluating the achievement of the project against the initial problem?
    These criteria are justified?
    The criteria have been used professionally to judge whether the problem has been solved?


Presentation: Have I ...

    Given the report an appropriate title?
    Structured the report appropriately, with appendices used for peripheral content and a single references list containing only sources referred to in the report?
    Written in a style appropriate to the computing audience?
    Written in a consistent manner e.g., tense, use of acronyms, citation style?
    Conformed to the requirements for page layout, font size, page limit etc. ?
    Ensured that all material included is correctly attributed?


Self-appraisal: Have I...

    Considered how my work could be extended?
    Included mature personal reflection which leads to lessons learnt?
    Suggested how the problems encountered might be avoided?
    Considered legal, social, ethical and professional issues, with justification if one or more are not relevant?
\end{itemize}