
\chapter{Introduction and Background Research}

% You can cite chapters by using '\ref{chapter1}', where the label must
% match that given in the 'label' command, as on the next line.
\label{chapter1}
\section{Introduction}
% \begin{itemize}
    % \item Reinforcement Learning (RL) is based on the concept of learning through experience - through trial-and-error.
    % \item  This is akin to the way in which humans and animals learn new skills (\textcolor{red}{link to psychology}).
    % \item Motivate need for exploration
    % \item Exploration is a widely studied topic in RL, as it is necessary for learning. Although exploration methods exist based on optimism, \textcolor{red}{cite here}, intrinsic motivation, \textcolor{red}{cite here}, human interaction, \textcolor{red}{cite here} and information theory, \textcolor{red}{cite here}, in practice, random exploration is ubiquitous. Randomness precludes efficiency and prohibits explainability.
    % \item In contrast to RL, Automated Planning uses embedded knowledge of the environment, in the form of a model, to determine the optimal sequence of successive actions required to reach a goal. However, Planning relies the model to accurately represent  the environment - this cannot be guaranteed and therefore Planning can be quite fragile.
    % \item Combinations of Planning and RL have been developed in order to overcome the fragility of Planning and reduce exploration required for learning, such as DARLING \cite{AIJ16-leonetti}, where exploration is constrained to seemingly optimal states by reasoning on the model.
    % \item Discuss issues with current state of the art.
    % \item Within this work we explore the development of a framework that synergises planning and learning in order to drive and constrain exploration by making intelligent hypotheses about the environment, informed by the inherently inaccurate, but still useful, model, previous experience and environmental observations, rather than through randomness. The ultimate goal of this work is to mitigate the effect of the inherent inaccuracies in the model on the quality of learned behaviour; resulting in agents that can learn beyond the inaccuracies of the model, through intelligent exploration.
% \end{itemize}
Reinforcement Learning (RL) \cite{DBLP:books/lib/SuttonB98} is based on the concept of learning through experience; through trial-and-error. An agent learns how to behave in an environment by interacting with it and receiving reinforcement (both positive and negative) through a numerical signal called the reward. RL is akin to human and animal learning, and comes from the field of Psychology through the studies of operant conditioning \cite{nla.cat-vn2770732}, which have shown that human and animal behaviour can be shaped through positive and negative reinforcement.
\\Experience can only be gained by "trying new things", however it is infeasible to "try everything", especially in physical tasks of practical interest. Thus, there is a need for "exploration"; this is when the agent "tries new things" and learns the consequences of its actions. Exploration is a widely studied topic in RL, as it is necessary for learning. Although exploration methods based on optimism, such as UCRL \cite{NIPS2006_c1b70d96} and Fitted R-Max \cite{SARA07-jong}, intrinsic motivation, such as the use of Competence Maps \cite{NIPS1991_e5f6ad6c}, and Bayesian Methods, such as Bayesian Q-Learning \cite{10.5555/295240.295801}, random exploration is ubiquitous in practice. Randomness precludes efficiency, as sub-optimal actions may be continually evaluated even if they have been realised to be sub-optimal. Randomness also prohibits explainability, and does not imply intelligence.
\\Automated Planning (or just Planning) uses embedded knowledge of the environment, in the form of a model, to determine the optimal sequence of successive actions to fulfil a goal \cite{russelNorvig2003:aima, Lav06}. However, planning relies on the model to accurately represent the environment; which cannot be guaranteed, due to approximations and abstractions, and therefore planning can be quite fragile. A clear distinction between Planning and RL is that Planning relies on previously obtained knowledge, whereas RL relies on obtaining knowledge through experience.
\\Although Planning and RL take different approaches to decision making, they may be combined, which is known as model-based RL - which has been show to be very successful in recent years (\cite{silver2017mastering}, \cite{pmlr-v28-levine13}). Model-based RL can be explicit, where an agent plans over a learned model, or implicit where planning and learning is more tightly coupled \cite{MAL-086}, throughout this work we focus on the latter.
\\Forms of model-based RL have been developed that overcome the inherent inaccuracies of models and reduce the exploration required for learning by using the planner to constrain and inform exploration, such as DARLING \cite{AIJ16-leonetti}; which is a big inspiration for this work.
\\Within this work we explore the development of a framework that synergises planning and learning in order to drive and constrain exploration by making intelligent hypotheses about the environment, informed by the inherently inaccurate, but still useful, model, previous experience and environmental observations, rather than through randomness. The ultimate goal of this work is to mitigate the effect of the inherent inaccuracies in the model on the quality of learned behaviour; resulting in agents that can learn beyond the inaccuracies of the model, through intelligent exploration.


\section{Reinforcement Learning}
Reinforcement Learning (RL) does not fall into either of the traditional machine learning paradigms (supervised and unsupervised learning) - it is a machine learning paradigm of its own. A RL problem comes in the form of a sequential-decision making problem, and is formalised through a Markov Decision Process (MDP). Within an RL problem a goal-directed decision-making agent learns how to behave in an environment, which may be stochastic. The agent learns by interacting with the environment through actions and observing the affects through its new state and a numerical reward signal. The goal of the agent is to learn how to map states to actions in order to maximise the cumulative long-term reward signal \cite{DBLP:books/lib/SuttonB98}. The behaviour that the agent learns is known as the \textbf{policy}. The \textbf{reward function} indicates the immediate value of state-action pair, the goal of the agent is to maximise the cumulative returns from this. The \textbf{value function} indicates the expected cumulative reward the agent can receive starting from a given state.
\\Within this work, we split RL into two categories: model-free and model-based. Model-free RL is the traditional instantiation of RL - the agent learns to act in an environment, with no knowledge of its dynamics. We briefly mentioned model-based RL within the introduction, but didn't explain what it actually is. Model-based RL is where the agent learns to act in an environment, and has some understanding of the dynamics of the environment in the form of a model. By the nature of models, the model is inaccurate, more often than not.

% \\Within the introduction, we briefly introduced model-based RL
% A Model-Free RL agent has 3 elements:
% \begin{itemize}
%     \item \textbf{Policy}
%     \item \textbf{Reward}
%     \item \textbf{Value}
% \end{itemize}
% A Model-Based RL agent has the same elements as that in the Model-Free setting, but additionally it has a Model. The model may be learnt by the agent in order to plan on, or it may be given to the agent to inform exploration.
% Within the Introduction we motivated the need for exploration, however we did not mention a key problem in RL; the \textit{exploration-exploitation trade-off}. The agent needs to explore in order to gain experience and learn, but it must also exploit its learned knowledge - the problem is knowing when to explore and when to exploit.
\subsection{Markov Decision Processes}
The Markov Property states that the future is conditionally independent of the past given the present. An RL problem that satisfies the Markov Property is known as a Markov Decision Problem, and can be modelled by a Markov Decision Process (MDP). Where an agent is able to fully observe its state, the problem can be modelled as an MDP. Conversely, where an agent can only partially observe its state, the problem can be modelled by a Partially Observable Markov Decision Process (POMDP). Consider an agent interacting with a stochastic gridworld, the agent can easily observe its state, whereas a robot navigating a maze may not be able to observe its exact state, due to uncertainty in sensors, joint readings, etc. In fact, the real-world is a POMDP. Within this work, as a simplification, we assume that the agent is fully able to observe its state. Furthermore that the environment can be discretised (rather than being modelled in a continuous nature); hence we consider \textbf{finite} MDPs.
A finite MDP is a 4-tuple: $\text{MDP} = (S,A,T,R)$ where:
\begin{itemize}
    \item $S$ is a finite set of states.
    \item $A$ is a finite set of actions.
    \item $T : S \times A \times S \rightarrow [0,1]$ is the transition function, which determines the probability of transitioning from a state $s \in S$ to $s' \in S$ with an action $a \in A$.
    \item $R:S \times A \times S \rightarrow \mathbb{R}$ is the reward function, which determines the reward signal, $r \in \mathbb{R}$ received by the agent from transitioning from a state $s \in S$ $s' \in S$ with the action $a \in A$. This reward is extrinsic to the agent; it comes from the environment.
    \item $\gamma$ is the discount factor.
\end{itemize}
The transition function, $T$ is a key indicator about the nature of the environment.
If $\forall s,s' \in S, \forall a \in A$, $T(s,a,'s) \in \{0,1\}$, then the environment is deterministic, otherwise it is probabilistic.
A deterministic environment is one which there is no variance in the outcomes of action in a given state; taking the same action in the same state always produces the same outcome. Whereas a probabilistic (or non-deterministic) environment has uncertainty associated with transitions.
\\The Bellman Equation determines the expected reward for being in a state $s \in S$ and following a fixed policy $\pi$:
$$V^\pi(s) = R(s, \pi(s)) + \gamma \sum_{s'}P(s'|s,\pi(s))V^\pi(s')$$
Where $V^\pi$ is the value function of the policy, $\pi$, $0 \le \gamma \le 1$ is the discount factor.
The Bellman Optimality equation determines the reward for taking the action giving the highest expected return.
$$V^{\pi*}(s) = \text{argmax}_a{R(s,a) + \gamma\sum_{s'}P(s'|s,a)V^{\pi*}(s')}$$
Where $V^{\pi*}$ is the value function of the optimal policy, $\pi*$, $0 \le \gamma \le 1$ is the discount factor.
\subsection{Dynamic Programming}
\begin{itemize}
\item Given a perfect model of the environment, embedded in a MDP, an optimal policy can be computed using Dynamic Programming. However, this assumption of a perfect model is flawed.
\end{itemize}
\subsubsection{Policy Iteration}
\subsubsection{Value Iteration}
\subsection{Temporal Difference Learning}
The (temporal) credit assignment problem \cite{Minsky:1961:ire} is the problem of determining which actions led to an outcome, and assigning credit among them; it's often the case that a sequence of actions led to an outcome, rather than a single action. In the context of RL, temporal credit assignment is important because in order to maximise the cumulative long-term reward, the agent needs to know which actions will realise such outcome. Temporal Difference (TD) \cite{10.5555/911176, 5392560} learning uses this concept; learning is driven by the error/difference between temporally successive predictions, so learning occurs whenever there is a change in prediction over time. It's a method for learning to predict; learning a prediction from another later learned prediction.
TD Learning algorithms are model-free.
TD Learning algorithms can be on-policy, where the value of the policy being currently carried out by the agent is learnt, or off-policy, where the value of the optimal policy is learnt independently of the agent's actions \cite{PooleMackworth17}.
% \\ TD(0) \cite{10.1023/A:1022633531479}
% \begin{itemize}
%     \item The (temporal) credit assignment problem.
%     \item Temporal Difference (TD) learning is driven by the error/difference between temporally successive predictions; learning occurs whenever there is a change in prediction over time. 
%     \cite{Sutton:1988}
%     \item Only relevant in multi-step prediction problems.
%     \item Temporal difference methods bootstrap from previous experience.
%     \item TD learning is a method for learning to predict.
%     \item Learnign a prediction from another later learned prediction
%     \item TD $\lambda$, TD0
% \end{itemize}
\subsubsection{Q-Learning}
Q-Learning \cite{Watkins:1989, journals/ml/WatkinsD92} is an off-policy Temporal Difference Learning method. Q-Learning is defined by:
$$Q(s_t,A_t) \leftarrow Q(s_t,a_t) + \alpha[r_{t+1} + \gamma \max_aQ(s_{t+1}, a) -Q(s_t,a_t)]$$
\subsubsection{SARSA: On-Policy TD-Learning}
SARSA \cite{rummery:cuedtr94, conf/nips/Sutton95} is an on-policy Temporal Difference Learning method. SARSA is defined by:
$$Q(S_t,A_t) \leftarrow Q(s_t,a_t) + \alpha[r_{t+1} + \gamma Q(s_{t+1}, a_{t+1})-Q(s_t,A_t)]$$
    % \item SARSA is an on-policy TD-Learning method.
\section{Planning}
\begin{itemize}
    \item Planning involves reasoning on a model of an environment in order to produce a sequence of actions that will achieve a goal.\cite{russelNorvig2003:aima}.
\end{itemize}
\subsection{A* Search}
\begin{itemize}
    \item A* Search \cite{4082128} is not necessarily a Planning algorithm, rather it is a search algorithm. However, a simple Planning agent with the purpose of navigation in a discretised state space can use A* for planning.
    \item Heuristic
    \item Admissable
\end{itemize}
\section{Exploration in Reinforcement Learning}
Thrun \cite{Thrun-1992-15850} distinguished exploration methods into two categories: directed and undirected. A more recent work distinguished between reward-free and reward-based exploration \cite{DBLP:journals/corr/abs-2109-00157}.
\subsection{Random}
The most common use of randomness in exploration is through $\epsilon$-greedy \cite{Watkins:1989, conf/nips/Sutton95}, which aims to balance the exploration and exploitation through an $\epsilon$ factor, such that the agent exploits its learned knowledge with probability $\epsilon$, and explores randomly with probability $1-\epsilon$. A common thing is to decay $\epsilon$ temporally, so the agent explores a lot early on, and then exploits more after it has learnt for a while.
Whilst this does provide a balance between the two extremes of pure exploration and pure exploitation, it results in continually evaluating sub-optimal actions long after they have been realised to be sub-optimal.
\\$\epsilon z$-greedy \cite{dabney2021temporallyextended}
\\Softmax \cite{10.1007/978-3-642-76153-9_28}
\\Random walk \cite{anderson86, NIPS1989_17000029}
\subsection{Optimism}
\subsection{Intrinsically Motivated}
\subsection{Deliberate}

% \begin{itemize}
%     \item $\epsilon$-greedy 
%     \item 

% \subsection{Directed}
% \subsubsection{Intrinsically Motivated}
% \subsubsection{Optimistic}
% \subsubsection{Deliberate}
% \subsection{Undirected}
% \subsubsection{Blind Exploration}
\section{Related Work (Planning and Learning)}
\begin{itemize}
    \item DARLING
    \item Dyna
    \item AlphaGo?
\end{itemize}
